Appendix A

### 2020-10-04 appendixA/appendixA.Rmd
progress with insets for density plots

```{r fig.width=12, fig.height=5}
ind_dens_plot <- df %>%
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.055) +
  labs(title = "Individual") +
  theme_classic()

fam_dens_plot <- df %>%
  filter(., fam_g != "unknown") %>% 
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.055) +
  labs(title = "Family") +
  theme_classic()

ggarrange(ind_dens_plot, fam_dens_plot)

>>>>

```{r fig.width=12, fig.height=5}

zoom_dims <- c(110, 210, 0, 0.01)
annot_xy <- c(50, 250, 0.02, 0.04)

ind_dens_plot <- df %>%
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = "blue") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = "blue") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
  geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
  ylim(0, 0.055) +
  xlim(0, 250) +
  labs(title = "Individual") +
  theme_classic()

ind_dens_plot +
  coord_cartesian(
    xlim = zoom_dims[1:2],
    ylim = zoom_dims[3:4]) +
  theme(title = element_blank()) -> ind_zoom

ind_dens_plot +
  annotation_custom(grob = ggplotGrob(ind_zoom), xmin = 50 , xmax = 250 , ymin = 0.02 , ymax = 0.04) -> a

fam_dens_plot <- df %>%
  filter(., fam_g != "unknown") %>% 
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = "blue") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = "blue") +
  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
  geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
  ylim(0, 0.055) +
  xlim(0, 250) + 
  labs(title = "Family") +
  theme_classic()

fam_dens_plot +
  coord_cartesian(
    xlim = zoom_dims[1:2],
    ylim = zoom_dims[3:4]) +
  theme(title = element_blank()) -> fam_zoom

fam_dens_plot +
  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = 100 , xmax = 200 , ymin = 0.02 , ymax = 0.05) -> b

ggarrange(a, b)
